Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2017-07-22 Response.tex

\begin{enumerate}
    \item
        \begin{itshape}
            In the statement "In addition, non-Keplerian orbits and multi-body dynamics have been shown to allow for a much greater range of potential
            missions at a reduced energy cost [15]" - you may want to reference, for example, the Lunar Ice Cube mission paper which absolutely requires low-thrust propulsion and non-keplerian dynamics to satisfy its mission objectives.

            Folta, D., Dichmann, D., Clark, P., Haapala, A., and Howell, K., "LunarCube Transfer Trajectory Options," AAS/AIAA Space Flight Mechanics Meeting, Williamsburg, Virginia, January 11-15, 2015.
        \end{itshape}

        Thank you for the comment and the additional reference.
        In addition to this change we have made other modifications to the introductory paragraphs to improve the organization and clarity.
        Specifically, the first paragraph has been divided, which motivates the use of electric propulsion and the advantages of small satellites which use electric propulsion.
        In addition, the suggested reference has been included in the paper.
        The modified paragraphs are duplicated below.

@@

\begin{correction}

Finally, there is no closed form analytical solution for the three-body problem and there are an insufficient number of analytical constants~\cite{szebehely1967}.
As a result numerical methods are often required to investigate solutions to the three body problem.
\end{correction}

\item 
    \begin{itshape}
"These techniques suffer from numerical instability and energy drift behaviors which make them ill-suited for long-term propagation. These dissipative effects are even more detrimental with the addition of low-thrust propulsion to the dynamic equations of motion."  It really depends on what you mean by "long term".  If transfers are on the order of hundreds of days, then high precision runge-kutte integrator, for example a Runge-Kutte Verner 8(9), can maintain suitable accuracy such that the energy drift in the Hamiltonian is very small, as can be seen in some of the references that the authors have cited.  If, on the other hand you mean 10-100's of years or more, i.e., when you create your Poincare maps, then this drift is more apparent.  I think that this statement needs to be quantified better because it gives a dishonest portrayal of high-precision Runge-Kutte integrators without numbers attached to it.
\end{itshape}

Thank you for the comment. 
The claims about the variational integrator have been qualified with some additional detail.
The correction is copied below.
\begin{correction}
As a result, these methods suffer from numerical instability and energy drift behaviors which make them ill-suited for the long-term propagation, e.g. on the order of decades to centuries, which is typical of the three-body problem. 
\end{correction}

### 2017-07-22 Response.tex

\item
    \begin{itshape}
"Conventional integration techniques fail to capture the physical laws and geometric properties of the dynamic system [8]. As a result, the long term effects of low-thrust on the spacecraft trajectory are not accurately captured."  Again, I think situationally I would disagree.  Transfers on the order of 100's of days can maintain accuracies of 1e-10 (nondimensional units) in the Hamiltonian, which is generally considered a "small" amount of energy drift.
\end{itshape}

These sentences have been modified and combined to enhance clarity and reduce some of the unecessary bloat. 
In addition, some additional detail has been added to explicitly define the notion of ``long-term'' in the context of numerical integration.
The modifications are copied below.
\begin{correction}
    Conventional Runge-Kutta integration techniques, such as those implemented in~\cite{mingotti2011,grebow2011}, fail to capture the physical laws and geometric properties of the dynamic system.
    As a result, these methods suffer from numerical instability and energy drift behaviors which make them ill-suited for the long-term propagation, e.g. on the order of decades to centuries, which is typical of the three-body problem. 
\end{correction}

\item 
\begin{itshape}
- "[15,25] have illustrated the rich structure that exists in the three-body problem." 
- "[23,6] implement the solutions using conventional Runge-Kutta integration techniques."
I don't think you can grammatically begin a sentence with reference numbers.  Please fix all instances of this.
\end{itshape}

Thank you for the comment.
Evidently in some styles, such as \href{https://www.dlsweb.rmit.edu.au/lsu/content/1_studyskills/study_tuts/apa_ll/position.html}{APA}, it is acceptable to start with a reference.
We agree that it is not the best with the numeric style citations.
The sentences have been reworded to avoid starting with a reference number. 
The corrections are shown below.

@@

Thank you for the clarification.
The sentence has been modified as follows.

\begin{correction}
It has been shown that there exist multi-dimensional structures, termed invariant manifolds, of constant energy trajectories that span the state space. 
\end{correction}

\item 
    \begin{itshape}
-"In this paper, we propose a systematic design method which enables low-thrust transfers in the planar circular restricted three-body problem." Why planar?  For simplicity?  Almost all parking orbits departing the Earth are likely going to have some inclination with respect to the rotating reference plane, and will likely require some three-dimensional thrusting to target the manifold.  You may want to indicate that this is a first step in the research to exploit the Poincare sections more easily, which is why I'm assuming it was done.  It doesn't hurt to be straightforward about this, as it is a first-step towards characterizing the design space.
\end{itshape}

Thank you for the comment.
The PCRTBP was primarily chosen as a simple dynamic system which still captures the primary structure of the three-body problem.
The introduction has been modified with an additional sentence indicating our use of the planar three body problem

@@

Thank you for the comment.
Some additional detail has been included mentioning the difficulties in applying the \Poincare~section approach to the 3D case.

\begin{correction}
While the \Poincare~section is well defined for the planar case, as a 2D representation, it is more challenging to implement and visualize for the general 3D three-body problem.
\end{correction}

\item
    \begin{itshape}
-"This discrete update map, or variational integrator, shares the same geometric properties of the continuous time system and exhibits much better energy behavior than the traditional integration methods, especially over long transfer durations with small magnitude control inputs."  Yes, but the order of the variational integrator still matters.  The drift in the state vector accuracy is still important to a mission designer, even if it is guaranteed to lie on an energy surface.  I think you should indicate that this is more for preliminary analysis to characterize the transfers, when this drift in state vector accuracy is tolerable.  I.E., it's useful for the introductory phases of mission design when trying to globally characterize the design space.  Characterizing the scope of the analysis in this way would be helpful to the audience.
\end{itshape}

Thank you for the comment.
The section on the variational integrator has been reduced and this specific sentence has been removed. 
However, additional detail has been provided in a the variational integrator subsection which discusses this drawback.

@@

Thank you for the comment.
This sentence has been removed from the introduction.

\item
    \begin{itshape}
Authors may also want to point out the loss of accuracy in variable step integrators that can also degrade first-order gradient based methods.  I didn't see this anywhere and it's something that should be acknowledged.  Basically, variable step integrators will introduce artificial "noise" into the gradients:

Pellegrini, E.P., Russell, R.P., On the Accuracy of Trajectory State Transition Matrices, Paper AAS-15-785, AAS/AIAA Astrodynamics Specialist Conference, Vail, CO, Aug 2015
\end{itshape}

Thank you for the comment and helpful reference.
Additional detail has been included in the manuscript discussing this potential drawback of variable step integrators.
j
\begin{correction}
In addition, it has been shown that variable step integrators, such as \texttt{ODE45} in Matlab, tend to degrade first-order gradient based methods, such as those used in~\cref{sec:optimal_control}~\cite{pellegrini2016}.
The fixed step size of the presented variational integrator mitigates the artifical ``noise'' of variable step integration schemes in gradient computation.
\end{correction}

\item 
    \begin{itshape}
"This results in an optimal solution rather than the suboptimal solution typical of direct optimal control methods." I disagree that suboptimality is typical of direct methods.  A direct method will typically solve the KKT conditions, which can be directly transcribed into the costates in the optimal control problem.  A direct method fully satisfying the KKT conditions can map to the indirect problem. If you want to strengthen this argument, then you should argue that it applies to direct methods which rely on coarse or suboptimal representations of the control.  For example, a hybrid direct method could use continuous optimal control theory control law, but directly minimize the cost function instead of solving the full TPBVP.  
\end{itshape}

Thank you for the comment.
The suboptimal claims of direct optimization has been reduced and modified.
Additional detail has been included on the merits of indirect optimal control vs. direct optimal control methods.
\begin{correction}
This results in an optimal solution rather than the suboptimal solution typical of direct optimal control methods which rely on course or suboptimal control parameterizations.
For example, a hybrid direct method may use a continuous control law developed from indirect optimal control theory while directly minimizing a cost function instead of solving the full two-point boundary value problem~\cite{ozimek2010a}.
\end{correction}

@@

\item 
    \begin{itshape}
Figure 1 should probably have "axis equal" applied to it.  For that matter, please check all trajectory plots (those which plot the position state), and ensure that all plots are using "axis equal".  If not, please regenerate those plots. 
\end{itshape}

Thank you for the comment.
All of the figures showing position states have been modified to use \texttt{axis equal}.

\item 
    \begin{itshape}
Section 3.1 has been discussed in many references, the reader may want to direct them to this material.
(Choose one of Marsden or West's papers for example.)
\end{itshape}

Thank you for the comment.
The discussion on the variational integrators has been reduced. 
Much of the background material on Lagrangian mechanics is removed and an additional paragraph is included to summarize the key ideas of variational integrators. 
In addition, the variational integrator details are moved into a titled subsection.
The additional paragraph is shown below.

@@

Consider the autonomous mechanical system described by the Lagrangian, \( L(q, \dot{q} ) \), for the generalized coordinates, \( q\) and velocities \( \dot{q} \).
The integration of the continuous Lagrangian along a path, \( q (t) \), followed by the system must satisfy Hamilton's principle, which results in the well-known Euler-Lagrange equations~\cite{lanczos1970}.
In the discrete time scenario, the continuous path \( q(t), \dot{q}(t) \), is replaced by a finite difference approximation over a fixed time step, e.g. \( q_0, \frac{q_1 - q_0}{h} \), which converges to the true velocity as \( h \) tends towards zero.
In this manner, we define a discrete Lagrangian, \( L_d (q_0, q_1, h) \) which approximates the integral of the true Lagrangian over the time interval \( h \) between \( q_0 \) and \( q_1\)~\cite{marsden2001}.
\end{correction}

\item 
    \begin{itshape}
The second-order trapezoidal rule will give significantly poorer state vector accuracy with respect to a high-precision RK integrator, even if the state is guaranteed to lie on an energy surface.  Why didn't the authors consider going to a higher-order variational integrator, or even a Taylor Integrator?  It is very likely that the integration accuracy will introduce some errors in the accuracy of the partial derivatives and in the states.
\end{itshape}

We chose the trapezoidal rule as it provides a second order quadrature approximation.
Furthermore, instead of using Taylor methods or higher order options, the trapezoidal rule provides an explicit second order accurate integration rule.
This greatly reduces the complexity of the optimization routine.
In addition, the background material on the variational integrators have been removed from the manuscript. 
Only the specific details covering the development of the variational integrator for the PCRTBP are discussed.

@@

\item 
    \begin{itshape}
Section 3.2 - please cite a reference as to where the selected quadrature rules presented in Table 1 have been derived.
\end{itshape}

In the interest of conciseness and to avoid repeating material that has already been covered in the literature, the discussion on variational integrators has been substantially reduced.
The background material on the variational integrators has been removed and this table has also been removed from the manuscript.

@@

\item 
    \begin{itshape}
Figure 2 - x-axis has no label but I think it's nondimensional time, please indicate.  Label all axes even if they are nondimensional units.
\end{itshape}

Thank you for the comment. 
All of the plots have been updated to include all axes labels.
Furthermore, the specific plot in questions has been replaced with another plot more explicitly showing the benefits of variational integrators over conventional integration schemes.
This modified plot is shown below.

\begin{correction}
    \begin{figure}[H] 
        \centering 
        \subcaptionbox{Earth-Moon three-body trajectory used for integrator comparision: A stable trajectory is used to test the variational and conventional integrators. 
        The energy level is high enough to enter the vicinity of the Moon but not escape the three body system.}
        [0.5\textwidth]{\includegraphics[width=\textwidth, height=0.2\textheight, keepaspectratio]{trajectory}}~
        \subcaptionbox{Mean Jacobi integral deviation between variational integrator and Matlab \texttt{ODE45}: A range of fixed step sizes are used for the variational integrator to approximately match the computational time of \texttt{ODE45}}
        [0.5\textwidth]{\includegraphics[width=\textwidth, height=0.2\textheight, keepaspectratio]{figures/cputimevsE.pdf}}~
\end{figure}
\end{correction}
\item 
    \begin{itshape}
I recommend removing appendix B.  Giving the equations and stating that the Matrix inversion is from Gauss-Jordan elimination is probably sufficient, unless there is some compelling algebraic manipulation that is very unique to the problem.
\end{itshape}

### 2017-07-23 Response.tex

Thank you for the comment.
The additional clarification has been added to the manuscript and copied below.
\begin{correction}

Over long simulation horizons or with the addition of small control inputs the inability of conventional integration schemes to accurately track the system energy limits the applicability of conventional techniques in which energy conservation is mandatory for characterizing the solution space.
\end{correction}

\item 
    \begin{itshape}
Section 5 - This method, while very useful in its given context is highly dependent on the use of the PCRTB in the framework of the current analysis.  This needs to somehow be conveyed.  3D transfers are significantly more challenging when it comes to exploiting Poincare sections.  It can be done, but more subplots, dimensions, and data storing are necessary to view the subspace - save to say, it is a more challenging endeavor that must be acknowledged for general purpose low-thrust mission design.
\end{itshape}

Thank you for the comment.
An additional paragraph has been added to the beginning of the mathematical background section which discusses our reachability based transfer approach.
This additional content is copied below.

@@

\begin{correction}
The numerical examples presented in this section are designed in the context of the PCRTBP.
The dynamic environment has a four dimensional state space and offers a convient integration constant in the form of the Jacobi integral.
As a result, there are well defined methods to define and exploit \Poincare sections, which result in straightforward two-dimensional subspaces of the system.
Our approach uses the \Poincare section to approximate the reachability set on this reduced subspace.
As a result, this approach is more difficult to apply to three-dimensional transfers in the general three body problem.
\Poincare sections in the case of the general six dimensional state space are significantly more challenging and typically require more complicated visualization techniques. 
However, this is an area of active research and some of the authors future research is aimed at implementing this approach for non-planar transfer trajectories.
\end{correction}

\item
    \begin{itshape}
Figures 10D and 13D - the authors need to present these plots in dimensional coordinates so that they may be reconciled with what existing technology can produce.  I recommend Newtons or milliNewtons.  For example, the NEXT (NASA evolutionary xenon thruster) can produce 0.25 Newtons of thrust at maximum power (~7 kW).  The XR5 Hall thruster can produce comparable thrust at 4.5 kW of power.  These are currently the highest-power single engines other than the ARM Hall thruster which is not flight ready yet.  For these examples to be reconciled against the capability of existing technology, we need to see the required forces that are being demanded from the optimal control problem.  It may be that the results are beyond the scope of current technology - that's fine - just say that they are examples and that it's ongoing work to formulate example problems that capture existing technology better.
\end{itshape}

Thank you for the comment.
The mentioned plots of the control input have been modified to show the data in dimensional units (Newtons). 
Some additional detail has been provided in the manuscript which discusses the choice of \( u = 0.75 \) and it's realtionship to the current state of the art thruster systems.
The modified plots are not included here but the additional content is copied below in response to a different but related comment.

\begin{correction}
Next, we determine the reachability set with the addition of a low thrust control input.
We define a maximum magnitude of the thrust as \( u_{max} = 0.75 \) and assume we can point the thrust in any direction within the plane. 
This model is representative of many spacecraft which have a body fixed thruster and attitude control system.
We assume a fully actuated spacecraft model which decouples the translational and rotational dynamics.
This acceleration limit is approximately \( u_{max} = \SI{2}{\milli\meter\per\second\squared} \) in the Earth-Moon system.
Assuming a fixed spacecraft mass of \SI{500}{\kilo\gram}, this model defines a maximum thrust of \SI{1}{\newton}.
Currently, the NASA NEXT xenon thruster is able to provide approximately \SI{0.25}{\newton} of thrust, and a cluster of such engines could be used to provide the desired thrust used in this work~\cite{schmidt2008}.
The trajectories are generated from a fixed initial state of \( \vecbf{x}_0 = \begin{bmatrix}0.8156 & 0 & 0 & 0.1922 \end{bmatrix}^T \) over a fixed time span of \( t_f = 1.4 \).
This initial state lies on the initial periodic orbit and the time of flight is equivalent to one half period of the initial periodic orbit. 
\begin{figure}[H]
    \centering
    \subcaptionbox{Control input for the selected transfer trajectory}{\includegraphics[width=0.5\textwidth]{control_input_l1}}~
    \subcaptionbox{Control Input: Combined control history for each stage of the reacability analysis. 
    The control always remains within the maximum bound.}{\includegraphics[width=0.5\textwidth]{figures/control_input_geo.pdf}}
\end{figure}
\end{correction}

### 2017-07-23 Response.tex

Thank you for the comment.
Additional detail has been incorporated which discusses the specific solver used in computing the solutions. 
The description does not specifically mention all of the possible options in \texttt{fsolve} but rather gives the key components used in our solution.
This approach seems to be consistent with the literature, e.g.~\cite{ozimek2010a,stuart2010}.
The modified portion is copied below.

\begin{correction}
In this work, we use the Matlab nonlinear solver \texttt{fsolve} to solve the system of nonlinear equations defined by the multiple shooting algorithm.
Within \texttt{fsolve}, we use the trust-region dogleg solver which makes use of the Powell dogleg procedure for computing a step direction and magnitude to minimize successive iterations of the solver.
All numerical integration is performed using the discrete variational integrator described in~\cref{sec:discrete_var}.
\end{correction}

\item
    \begin{itshape}
Did the authors experiment with the number of multiple shooting stages in their example problems?  There must be some sort of "sweet spot" in number of stages for the example problems attempted.  If I missed it, I apologize, but I didn't see it.
\end{itshape}

We did spend considerable time in determining the appropriate number of stages. 
One key issue was that our implementation in software depended on dividing the total number of integration steps by the number of interior stages.
For simplicity, this reduced the possible number of stages to an even number. 
Additionally, we discovered that adding many stages tended to degrade the solution and cause difficulties in covergence. 
The solver would tend to ensure a continuous trajectory, by satisfying the interior stages, at the expense of the terminal stage. 
Some additional detail has been provided that mentions our choice of the number of stages and has been copied below.

@@

\begin{correction}
Based on experimentation, we use four stages in our multiple shooting method.
This provided the best performance and convergence stability while minimizing the difficulties in additional interior constraints.
\end{correction}

\item 
    \begin{itshape}
Section 6.1 - I don't think you need to explain how you created the three-body orbits.  This can be found in many references - You can just cite a reference and give the orbit specifications.  (Starting with line 49, page 18, up to line 21 page 19.)
\end{itshape}

Thank you for the comment.
The discussion of generating periodic orbits in the three body problem has been removed.
It is replaced with a small introduction mentioning the differential correction process and a citation to a relevant resource. 
The revised paragraph is copied below.

@@

There is additional research to extend these results to more general transfer scenarios in future work.
The incorporation of fourth body perturbations, such as the Sun in the Earth-Moon system, offers an additional method of increasing the reachable set with the combined use of the solar perturbation and low-thrust propulsion.
In addition, the assumed acceleration magnitude is currently beyond the capabilities of current electric propulsion systems.
Furthermore, this analysis did not consider the effect of variable mass on the optimal control solution.
This will result in a more complicated optimal control problem and is a focus of future research.
Finally, Lyapunov control theory, which has previously been applied to the two-body problem, is being investigated in the hope of designing closed loop control schemes for this three-body scenario~\cite{chang2002}.
The addition of attitude dynamics and realistic pointing constraints would significantly improve the applicability of this work.
\end{correction}

\item 
    \begin{itshape}
The authors should discuss some statistics of the convergence of their multiple shooting TPBVP - number of iterations, compute time, etc.
\end{itshape}

Thank you for the comment, howver it seems to be rare for the research community to give detailed description of the numerical optimization method.
Most of the literature tends to not spend time discussing the low level details of the computational procedure, e.g.~\cite{grebow2011,stuart2010}.
In addition, the number of iterations, computation time and even the eventual cost function value are highly dependent on the specific system and more specifically the implementation of the algorithm in software. 
There are a wide variety of works which are focused more exclusively on the computational implementation of various optimal control techniques which do spend significant time on the computational characteristics.
However, our manuscript is primarily focused on demonstrating the feasbility of using reachability sets to design transfer trajectories.
As a result, there is not much benefit to detailed statistics of the implementation of this methodology, and we have omitted it from the manuscript.

@@

\item
    \begin{itshape}
"Low energy transfers from the Earth to the Lagrange points are necessary for future missions."  One must be careful not to confuse these with traditional "low-energy transfers" to the moon, which use Sun third-body perturbations to transfer into lunar orbit.  These are what many mission designers define as "low-energy" lunar transfers.  This is actually a four-body problem (Sun, Earth, moon, spacecraft), and represents additional delta-V savings (as was done with NASA's GRAIL mission.)

Example:

Parker, J. and Anderson, R., "Low-Energy Lunar Trajectory Design," DEEP SPACE COMMUNICATIONS AND NAVIGATION SERIES, Jet Propulsion Laboratory Pasadena, California, July 2013.

Online Copy: https://descanso.jpl.nasa.gov/monograph/series12/LunarTraj--Overall.pdf
\end{itshape}

Thank you for the comment.
This sentence has been modified to make it more clear that we're discussing low thrust propulsion rather than low-energy transfers.
The modified sentence is copied below.

@@

\begin{correction}
Transfers from the Earth to the Lagrange points, through the use of low-thrust electric propulsion, offer an additional and potentially shorter time of flight in comparison to the low-energy transfers which utilize solar perturbations.
\end{correction}

\item 
    \begin{itshape}
For what it's worth, exploiting sun perturbations with low-thrust in the Earth-moon RTBP would be highly beneficial and represent a worthy avenue of future research (more on this below.)
\end{itshape}

Thank you for the comment.
This is a very interesting suggestion and something that we will take into consideration for future research.

### 2017-07-23 Response.tex

PAPER SUMMARY:
The contribution of the authors is the synthesis of reachability theory with traditional low-energy mission design approaches to ease the study of the low-thrust mission design space in the CR3BP.  A crucial point is that reachability analysis in non-integrable systems is typically limited by the dimensionality of the control parameterization, which can be extremely large for continuous-thrust problems, depending on the time discretization used.  The authors numerically probe the boundaries of the reachable space by optimizing a distance metric on the Poincare section, avoiding the extreme cost of unmotivated exploration.  Numerical experiments show how the method could be applied in two CR3BP orbit transfer scenarios.  For a multi-rev solution, the method is applied once per rev and the reachable end state with minimal distance to the target manifold is used as the basis for the next rev.

ASSESSMENT:

The central premise of the paper - using optimization of Poincare distance as a guiding motivation to make low-thrust reachability analysis more tractable - is interesting, useful, and to my knowledge reasonably novel.  Furthermore, the quality of the writing is good (at local scales) and there is an appropriate degree of literature review.  However, there are two major problems with this paper.
\end{itshape}
\begin{itemize}

\item 
    \begin{itshape}
First, in terms of composition, large portions of the paper are spent on lengthy development of foundational work that is well-known within the astrodynamics community and available in textbooks. 
\end{itshape}

\item 
    \begin{itshape}
        Secondly, the contributions and findings of the authors feel highly preliminary and do not seem to evaluate their method at significant depth.
    \end{itshape}

    Thank you for the comment. 
    The numerical examples are meant to demonstrate the use of this approach and the feasibility of using the reachability set on a \Poincare section to determine transfer trajecotries.
    The examples give two demonstrations of finding a transfer trajectory in the PCRTBP and demonstrate combining several iterations of the reachability set for a transfer.

\item
    \begin{itshape}
While there are the beginnings of a good article within this manuscript, it is not sufficiently close to publishable form to be accepted.  I recommend that the paper be rejected and that the authors push their investigation a bit further.  The eventual publication should focus less on background and should provide more insight into the fundamental properties of their method, using more rigorously constructed and analyzed examples.
\end{itshape}

\item 
    \begin{itshape}
I can sympathize that there was quite a long road to get to the point of understanding this topic and generating results in it. I hope that the authors will not find this verdict too discouraging, as I believe that stronger results are well within their reach.
\end{itshape}
\end{itemize}

@@

\item 
    \begin{itshape}
I can sympathize that there was quite a long road to get to the point of understanding this topic and generating results in it. I hope that the authors will not find this verdict too discouraging, as I believe that stronger results are well within their reach.
\end{itshape}
\end{itemize}

SPECIFIC FEEDBACK:
\begin{enumerate}
    \item
    \begin{itshape}
*** Bloat
In the introduction, the exposition of the problem could be considerably condensed, given the venue of publication. Additionally, the somewhat sprawling discussion jumps back and forth, and many key points seem to be repeated more than necessary.  It needs to be organized into titled subsections with specific scope.
\end{itshape}

Thank you for the comment.
The introduction is reduced and many of the paragraphs have been reworded and combined. 
In addition, the extended discussion of the benefits of variational integrators is removed from the introduction.
The mathematical background has been condensed into a single section with seperate subsections which discuss some of the mathematical details.
The background section is focused on reviewing the relevant material rather than reintroducing topics.
In the interest of space the reorganized section is omitted in this response.

@@

\item
    \begin{itshape}
The development of the CR3BP, invariant manifolds and Poincare maps, all go on a bit too long. These should be refreshers to the audience that expose the specific equations and concepts that you'll be leveraging, not full-on introductions to well-established areas.  Spending several pages on variational principles is way too much.
\end{itshape}

Thank you for the comment.
The mathematical background has been reduced and condensed into a single section with multiple subsections.
The discussion of the PCRTBP, invariant manifolds and \Poincare maps are combined into a single subsection.
Furthermore, the variational integrator discussion has been reduced and the background material on the derivation of variational mechanics has been omitted.
Instead, only the specific discussion of the development of the variational integrator is included.

\item
    \begin{itshape}
Section 4 ends on page 14 with essentially a thesis statement ("In this paper, we...").  Strive to push the boundary between background and new developments to a much earlier point in the paper; it shouldn't happen so late that you need to remind the audience what the paper is for.
\end{itshape}

Thank you for the comment. 
The introductory detail has been reduced and combined into a single section. 
As a result, the third section begins with the new contributions which describe the optimal control formulation of the reachability set.
